Gaussian variance estimation in simulated data sets

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

This script implements the "Gaussian variance estimation" simulation
experiments in the paper. In particular, we compare the Mean Field
Variational Bayes (MFVB) method against SMASH in two scenarios. The
figure and table generated at the end of this script should match up
with the figure and table shown in the paper.

@@

```{r analysis-settings-1}
nsim1 <- 10
nsim2 <- 10
```

@@

The following two tables shows the mean squared error (MSE) averaged
over the 100 simulations in each of the scenarios. Compare these
results with Table 1 in the paper.

```{r summarize-mse}
mse.table1 <- rbind(c(mean(mse.mu.uneven.mfvb),mean(mse.sd.uneven.mfvb)),
                    c(mean(mse.mu.uneven.smash),mean(mse.sd.uneven.smash)))
mse.table2 <- rbind(c(mean(mse.mu.even.mfvb),mean(mse.sd.even.mfvb)),
                    c(mean(mse.mu.even.smash),mean(mse.sd.even.smash)))
rownames(mse.table1) <- c("MFVB","SMASH")
colnames(mse.table1) <- c("mean","sd")
rownames(mse.table2) <- c("MFVB","SMASH")
colnames(mse.table2) <- c("mean","sd")
cat(sprintf("MSE averaged across %d simulations in Scenario 1:\n",nsim1))
print(mse.table1)
cat(sprintf("and averaged across %d simulations in Scenario 2:\n",nsim2))
print(mse.table2)
```

>>>>

This analysis implements the "Gaussian variance estimation" simulation
experiments in the paper. In particular, we compare the Mean Field
Variational Bayes (MFVB) method against SMASH in two scenarios. The
figure and table generated at the end of this script should match up
with the figure and table shown in the paper.

@@

```{r analysis-settings-1}
nsim1 <- 100
nsim2 <- 100
```

@@

The following two tables show the mean squared error (MSE) averaged
over the 100 simulations in each of the scenarios. Compare these
results with Table 1 in the paper.

```{r summarize-mse}
mse.table1 <- rbind(c(mean(mse.mu.uneven.mfvb),mean(mse.sd.uneven.mfvb)),
                    c(mean(mse.mu.uneven.smash),mean(mse.sd.uneven.smash)))
mse.table2 <- rbind(c(mean(mse.mu.even.mfvb),mean(mse.sd.even.mfvb)),
                    c(mean(mse.mu.even.smash),mean(mse.sd.even.smash)))
rownames(mse.table1) <- c("MFVB","SMASH")
colnames(mse.table1) <- c("mean","sd")
rownames(mse.table2) <- c("MFVB","SMASH")
colnames(mse.table2) <- c("mean","sd")
cat(sprintf("MSE averaged across %d simulations in Scenario 1:\n",nsim1))
print(mse.table1)
cat("\n")
cat(sprintf("MSE averaged across %d simulations in Scenario 2:\n",nsim2))
print(mse.table2)
```
